Mitigating Interest Flooding DDoS Attacks in Named Data Networking

### 2012-12-07 05-evaluation.tex
Small correction to make sure paper is compilable
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@848 df1a90cd-247b-4364-bdaf-287a704eb499
Initial part of the evaluation section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@870 df1a90cd-247b-4364-bdaf-287a704eb499

% \todo{Both simulation, as well as emulation for various sized topologies (trees as well as real topologies), various parameters etc.
% List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.

% Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers, Latency for good clients, good versus bad interests as a function of time).}

We want to explore the effectiveness of designed mitigation techniques in a two distinctive ways. First, we need to understand how each method works on a very ground level of a just few nodes and links. Second, we want to pick promising techniques and see if they work in a large scale networks of hundreds and thousands of nodes. To ensure the correct transition from small scale experiments to large scale experiments we had to use the same evaluation tool in order to eliminate any possibility of implementation discrepancy. As of today the only network simulator supporting full NDN logic is the NS-3 based ndnSIM software.

\input{small-scale}
\input{large-scale}

>>>>

% List all possible parameters, say clearly which ones we vary, and which ones we do not, along with explanations.

% Metrics that we will consider in our evaluation (Satisfaction rate for good clients, Link utilization near producers,

% alex: what's a point of latency?  it would matter only for queueing method and we not really pushing this method
% Latency for good clients, good versus bad interests as a function of time

In this section present an in-depth study, aiming to explore quality and effectiveness of the designed Interest flooding attack mitigation methods.
Our study is based on simulations performed with the help of open-source ndnSIM~\cite{ndnsim} package, which implements NDN protocol stack for NS-3 network simulator.\footnote{\url{http://www.nsnam.org/}}

% why we chose small scale topology
% what point we wanted to show we small scale
% what points we wanted to verify with larger-scale internet like topology

% Metrics
Quality of the attack mitigation methods directly corresponds to the quality of service for the legitimate users during an ongoing attack, which in NDN network can be quantified through percentage of satisfied Interest.
For example, if the network implements a mitigation method $X$ and under the attack majority of user-expressed Interests are getting satisfied, then the method $X$ can be seen as highly effective.
At the same time, if only a small percentage of the expressed Interest are getting satisfied during the attack, the method $X$ can be called ineffective.

% Traffic pattern
In our experiments we made a simplistic assumption that both legitimate users and adversaries express Interests with constant average rates with randomized (uniform distribution) time gaps between each two consecutive Interests.
% Alex: not sure how to argue about the traffic pattern
Although this pattern is not truly realistic, it gives us a good statistical mix of traffic from all network users without excessive network buffering.
In addition to that, in each run of the simulation we ensure that all Interests expressed by the legitimate users during a no-attack period are satisfied.
For simplicity and without losing any generality, we also equalized the average rates with which the legitimate users express Interests.

% Fixed parameters
The \emph{Delay} and \emph{Data size} parameters for the Interest limits calculation (1) were set to fixed values for every node in the simulated topology.
In particular, for the small-scale experiments we set Delay to 80~ms and for the large-scale experiments we used the value 330~ms (the order of the largest RTT).
Data size parameter was set to 1100~bytes for all simulation runs and topologies.

\input{eval-small-scale}
\input{eval-large-scale}

### 2012-12-07 eval-small-scale.tex
Modifying figures in evaluation
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@854 df1a90cd-247b-4364-bdaf-287a704eb499
Initial part of the evaluation section
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@870 df1a90cd-247b-4364-bdaf-287a704eb499

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.3]{topo-tree-evil-5-good-0-producer-gw}
  \caption{Small-scale topology (one of the runs with 30\% of attackers, all links are 10Mbps with randomized delay 1-10ms)}
  \label{fig:small-scale-topo}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=1]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw-dynamics-40}
  \caption{Satisfaction ratio dynamics during the attack (7 attackers / 9 legitimate)}
  \label{fig:small-scale-topo 3}
\end{figure}

>>>>

To assess baseline performance metrics of the designed Interest flooding attack mitigation methods, we evaluated them first using a simplistic small-scale binary tree topology (Fig.~\ref{fig:small-scale}).
All links in this topology were assigned 10~Mbps bandwidths with randomized propagation delays from the range from one to ten milliseconds.
Both legitimate users and attackers were placed only on leaf nodes (red), each expressing Interests towards a single producer placed at the root of the tree. 
% Alex: should we mention that?
The main reason to chose a binary tree topology was that it represents one of the worst cases to defend against flooding DDoS attacks.
That is, sharing of the network links exponentially increases as decreasing level of the binary tree.

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.2]{topo-tree-evil-5-good-0-producer-gw}
  \caption{Small-scale binary tree topology}
  \label{fig:small-scale}
\end{figure}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[scale=1]{tree-topo-var-evils-max-consumers-30mins/tree-good-0-producer-gw}
  \caption{Satisfaction ratio dynamics during the attack (7 attackers / 9 legitimate)}
  \label{fig:small-scale-topo 3}
\end{figure*}
